### 2013-12-14 inst/stuff/taxize_vignette.Rmd
udpated vignette to fix error, added margins file, added citaiton info to startup message

```{r resolvenames, eval=TRUE, cache=TRUE}
library(taxize)
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
temp[ , -c(1,4)]
```

@@

```{r tnrs, eval=TRUE, cache=TRUE}
mynames <- c("Helianthus annuus", "Pinus contort", "Poa anua", "Abis magnifica",
  	"Rosa california", "Festuca arundinace", "Sorbus occidentalos","Madia sateva")
tnrs(query = mynames)[ , -c(5:7)]
```

@@

```{r synonyms, eval=TRUE, cache=TRUE, message=FALSE, warning=FALSE, comment=NA}
mynames <- c("Helianthus annuus ssp. jaegeri", "Helianthus annuus ssp. lenticularis", "Helianthus annuus ssp. texanus")
tsn <- get_tsn(mynames)
library(plyr)
ldply(tsn, itis_acceptname)
```

@@

```{r itisclass, eval=TRUE, cache=TRUE}
specieslist <- c("Abies procera","Pinus contorta")
classification(specieslist, db = 'itis')
```

@@

```{r interactive, eval=TRUE, echo=TRUE, cache=TRUE}
get_tsn(searchterm = "Heliastes", searchtype = "sciname")
```

@@

```{r interactive_many, eval=TRUE, echo=TRUE, cache=TRUE}
splist <- c("annona cherimola", 'annona muricata', "quercus robur")
get_tsn(searchterm = splist, searchtype = "sciname")
```

@@

```{r downstream, eval=TRUE, cache=TRUE}
col_downstream(name = "Apis", downto = "Species")[[1]]
```

@@

```{r tax_match, cache=TRUE, tidy=FALSE}
A <- "gammarus roeseli"

>>>>

```{r resolvenames, eval=TRUE, cache=FALSE}
library(taxize)
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
temp[ , -c(1,4)]
```

@@

```{r tnrs, eval=TRUE, cache=FALSE}
mynames <- c("Helianthus annuus", "Pinus contort", "Poa anua", "Abis magnifica",
  	"Rosa california", "Festuca arundinace", "Sorbus occidentalos","Madia sateva")
tnrs(query = mynames, getpost="GET")[ , -c(5:7)]
```

@@

```{r synonyms, eval=TRUE, cache=FALSE, message=FALSE, warning=FALSE, comment=NA}
mynames <- c("Helianthus annuus ssp. jaegeri", "Helianthus annuus ssp. lenticularis", "Helianthus annuus ssp. texanus")
tsn <- get_tsn(mynames)
library(plyr)
ldply(tsn, itis_acceptname)
```

@@

```{r itisclass, eval=TRUE, cache=FALSE}
specieslist <- c("Abies procera","Pinus contorta")
classification(specieslist, db = 'itis')
```

@@

```{r interactive, eval=TRUE, echo=TRUE, cache=FALSE}
get_tsn(searchterm = "Heliastes", searchtype = "sciname")
```

@@

```{r interactive_many, eval=TRUE, echo=TRUE, cache=FALSE}
splist <- c("annona cherimola", 'annona muricata', "quercus robur")
get_tsn(searchterm = splist, searchtype = "sciname")
```

@@

```{r downstream, eval=TRUE, cache=FALSE}
col_downstream(name = "Apis", downto = "Species")[[1]]
```

@@

```{r tax_match, cache=FALSE, tidy=FALSE}
A <- "gammarus roeseli"
